 %1-2 paragraph overview of science goals.  BAO, RSD, other applications.
 %SDT2015 as starting point.

As discussed extensively in \S 2.2.4 of SDT15 (written by
members of our team), the defining goal of HLS spectroscopy is to derive
constraints on dark energy from a slitless spectroscopic (grism)
redshift survey of approximately 20 million emission line galaxies (ELG) in the redshift range $z=1-3$.
The galaxy redshift survey will enable high-precision measurements of the cosmic expansion history via BAO and structure growth via RSD.  
Acoustic oscillations in the pre-recombination universe imprint a characteristic scale on matter clustering, which
can be measured in the transverse and line-of-sight directions to
determine the angular-diameter distance $D_A(z)$ and Hubble parameter $H(z)$, respectively \cite{Blake03,Seo03,CW12}.  Anisotropy of clustering
caused by galaxy peculiar velocities constrains (in linear perturbation
theory) the combination $\sigma_m(z) f_g(z)$, where $\sigma_m$ describes
the rms amplitude of matter fluctuations and $f_g(z) \equiv d\ln\sigma_m(z)/d\ln a$ is the fluctuation growth rate.
Thus the GRS on its own can address the key questions identified by
NWNH: whether cosmic acceleration is caused by modified gravity
or by dark energy, and whether (in the latter case) the dark energy
density evolves in time \cite{Guzzo08,Wang08}.  These tests become more powerful in
combination with weak lensing and cluster measurements from HLS Imaging
and high-precision relative distance measurements from the Supernova
Survey \cite{dePutter:2013xda,dePutter:2013nha}. The broadband shape of the galaxy power spectrum and higher order
measures of galaxy clustering provide additional diagnostics of
dark energy, neutrino masses, and inflation, and insights on the physics of galaxy formation.  
%There are two largely distinct sources of systematics in the galaxy clustering program, associated with
%the uniformity of the GRS and with astrophysical modeling uncertainties.
%We discuss these in \S\ref{sec:grs_requirements} and~\S\ref{sec:grs_forecasting}, respectively, and we briefly
%discuss mitigation strategies in \S\ref{sec:grs_mitigation}.
While all aspects of our GRS investigation are interconnected, we
organize it in a structure similar to that of \S
\ref{sec:wl_gal-clusters} for clarity: requirements, simulations, and prototype pipelines in \S \ref{sec:grs_requirements},
cosmological forecasting, modeling, and cosmological simulations in \S
\ref{sec:cmethods}, and systematics testing and mitigation in \S \ref{sec:gal_syst}.

\input{subsection_galaxy_clustering_requirement_simulation.tex}

\subsection{Cosmological Forecasting, Modeling, and Simulations (D2, D8, D9)}
\label{sec:cmethods}
%================================================
%\Auth{Yun, Katrin, Nikhil, Rachel B, Alina, Shirley, Olivier}

\subs{Forecasting.} Our initial forecasts for the cosmological constraints from 
the WFIRST GRS will adopt the model-independent approach (incorporating
both BAO and RSD) that Co-I Wang has developed \cite{Wang2013} and
used for the WFIRST SDT reports and similar forecasts for Euclid \cite{WangEuclid2010}.
This approach offers a fast way to forecast how uncertainties in
$H(z)$, $D_A(z)$, growth rates, and other cosmological parameters
change in response to changes of the survey strategy, instrument
performance, or astrophysical inputs such as the H$\alpha$ luminosity
function.  Early in this investigation, we will incorporate a full description
of redshift-space galaxy clustering into \CoLi, using a halo
occupation density (HOD) framework similar to that already implemented for 
angular galaxy clustering \cite{Krause2013}.  In the medium term, we will also
incorporate effects of clustering measurement and theoretical
modeling systematics via nuisance parameters, analogous to our
existing treatments of observational and theoretical systematics
in weak lensing analysis.  The expected level of these systematics
will be informed by the studies described in \S\ref{sec:grs_requirements}
and below.  As with the imaging survey, this comprehensive forecasting
framework will enable us to connect low-level technical requirements
to our top-level science goals.

\subs{GRS modeling.} The development of the methodology for the
interpretation of GRS data is centered on the mitigation of the
astrophysical systematic effects  for galaxy clustering measurements:
nonlinear effects, RSD (growth rate signal on large scales and
contamination on small and intermediate scales),  and galaxy bias (the
difference between galaxy and matter distributions). 
Co-I Padmanabhan is a leading expert in BAO/RSD data analysis \cite{Padmanabhan2007,Padmanabhan2008,Padmanabhan2009,Padmanabhan2012,Xu2012}; he will lead our
work in GRS modeling/interpretation methods, with participation from the PI and Co-Is
Bean, Ho, Samushia, Spergel, Wang, and Weinberg \cite{CW12,Ho2012,Anderson2014,Wang2014,Osumi2015,Alam2015a,Alam2015b,Cuesta2015}.

BAO measurement is now a mature field, but WFIRST probes new regimes
of precision and redshift using different instrumental choices
and different classes of galaxy tracers from previous surveys.
Effects of non-linear clustering and galaxy bias are expected to
influence BAO measurements at the $\sim 0.5\%$ level \cite{Padmanabhan2009}, which is
significant compared to WFIRST statistical errors.
Reconstruction methods \cite{Eisenstein2007,Padmanabhan2012,Vargas2015}, 
which attempt to reverse the
nonlinear evolution of the BAO feature, appear to remove
most of this effect while simultaneously improving the precision
of BAO measurements.  Current observational studies use very simple
reconstruction algorithms.  We will explore more sophisticated
reconstruction methods, building on low redshift work \cite{Carrick15}, and test their performance on simulations
of WFIRST galaxy redshift catalogs, including realistic treatments of
survey geometry, redshift evolution, source space density, and
variable completeness.  Building on current work by Co-Is
\cite{Padmanabhan2012,Vargas2015,Osumi2015,Zhu2015}, 
we will also investigate improved clustering estimators that can sharpen the precision and improve the robustness
of BAO measurements.

In sharp contrast to BAO measurements, cosmological inference from 
RSD measurements is already limited mainly by uncertainties in 
theoretical modeling, with application of different models to the
same underlying data yielding differences at the $\sim 10\%$ level.
%{\bf SH: Not sure it is 5\% level, I think BOSS results differ by 
%nearly 10\% level with the mock challenge} .
Furthermore, the statistical signal-to-noise ratio of RSD measurements
increases rapidly with decreasing scale, so there are potentially
large gains from modeling that extends into the fully non-linear regime.
We will pursue a variety of approaches to improving and testing
RSD models, including the 
%{\bf not calling this brute force ? } ``brute force'' 
efficient method of computing predictions
numerically by populating the halos of N-body simulations with galaxies. 
Co-I Spergel has expertise in combining imaging and spectroscopic 
data to predict the relationship between galaxies and halos \cite{Hikage2012}.
One can think of this method as producing ``emulators'' \cite{Heitmann2014}
that predict galaxy clustering statistics as a function 
of cosmological parameters and parameters that describe the relation
between galaxies and dark matter halos.
The approach shows promise (e.g., \cite{Reid2014}),
but it relies on parameterized models for populating halos,
and the accuracy of these needs to be tested against galaxy catalogs
constructed in ways that do not share the same assumptions
(e.g., by semi-analytic models or abundance-age matching).
We will use similar techniques to investigate the impact of
non-linear evolution and bias on the broadband galaxy power
spectrum, and thus improve our ability to extract cosmological
information from this measurement.

Galaxy bias is likely scale-dependent; its testing will require realistic ELG mocks, and its mitigation will require 
the successful measurement of the higher-order statistics of galaxy clustering, which in turn requires a 
sufficiently high galaxy number density for the GRS. 
An essential difference between the WFIRST and Euclid spectroscopic
surveys is that due to the much smaller pixel scale (0.11$^{\prime\prime}$ for WFIRST
versus 0.3$^{\prime\prime}$ for Euclid) and larger telescope aperture, WFIRST 
is capable of carrying out a significantly deeper GRS, which can result in
%, at least as currently planned, is the 
a much higher space density of the WFIRST sample over most
of its redshift range.
This high sampling density represents a significant science opportunity
for WFIRST; 
in particular it will boost the significance of higher-order correlations. 
Building on previous work by members of our team \cite{Takada08,Schaan14,Dore14,Chen15},
%(Takada et al. 2008; Schaan, Takada \& Spergel 2014; Chen, Ho et al. 2015), 
we will investigate techniques that use the galaxy
bispectrum and other higher-order statistics to sharpen cosmological
constraints, by directly probing the matter density and velocity fields
and by improving knowledge of ``nuisance parameters'' that describe
galaxy bias.  We will examine ways that RSD measurement precision
can be improved by cross-correlating multiple tracer populations
with different clustering bias to suppress cosmic 
variance \cite{mcDonald2009,Bernstein2011,dePutter:2014lna}, weighting galaxies by mass
to suppress shot noise \cite{Seljak2009}, and building group catalogs
to collapse fingers-of-God \cite{Reid2010}.
We will investigate potential gains from cross-correlating the
WFIRST galaxy redshift catalogs with H$\,${\sc i} 21 cm ``intensity mapping''
measurements, or with CMB measurements, or (at $z>2$) the Ly$\alpha$ forest.
In all of these studies, we will pay particular attention to 
the influence of the sampling density, as this directly informs
the trade between depth and area in the GRS (see \S\ref{sec:sur_opt}).

\subs{Cosmological simulations.} The cosmological simulations described in \S\ref{sec:wl_methodology} 
will also be useful for the methodology development outlined above.
However, the optimal simulations for BAO and RSD studies will typically
be larger volume and lower resolution than those for weak lensing:
large volumes are needed for good statistics and to eliminate finite
box effects, but we do not need to model the small scale matter 
distribution or baryonic effects (which are encoded in the 
models used to populate halos with galaxies).  Furthermore, 
simulations tuned to the WFIRST GRS need only be evolved to $z=1$.
Co-I Ho will lead our cosmological simulations for the GRS, with participation from
team members Benson, Heitmann, Kiessling, Wang, and postdocs.

We will leverage the participation of several of our team members in 
Euclid and DESI to produce large simulated ELG catalogs,
building on work we have already begun for these projects.
To model emission-line selection, we will use both semi-analytic galaxy
formation models (SAM) and HOD models that are tuned to produce
observed number densities and clustering.
%The current Euclid ELG mocks are made using SAM, but are limited in emission line modeling 
%and simulation volume. 
We expect to be able to provide ELG mocks for WFIRST similar to those used 
by Euclid on a short time scale.
We will incorporate these into the early pixel-level 
simulations described in \S\ref{sec:grs_requirements},
which will in turn be used to assess impacts of incompleteness,
contamination, and redshift errors on the galaxy distribution.

We will base our first cosmological volume ELG catalogs on two very large simulations
that are already available to us through collaborator Heitmann: 
the Outer Rim simulation, covering
a volume of $4.225\,{\rm Gpc}^3$ with a particle mass of
$\sim 2\times 10^9 M_\odot$,
and the Q Continuum simulation, covering a volume of $1.3\,{\rm Gpc}^3$
with particle mass of $\sim 10^8 M_\odot$.
The Outer Rim simulation was used to create the simulated ELG
catalog for DESI.
We will combine the halo populations from these simulations with the
Galacticus SAM code \cite{Benson2010} to create clustered ELG catalogs,
some in fixed-redshift cubes for methodology tests and some in light cones
with realistic survey geometry and redshift evolution.
Our most ambitious simulation efforts, later in the investigation
period, will take full light-cone ELG catalogs, create pixel-level
simulations that span the entire HLS area, and analyze these simulations
with the proto-type pipeline to produce ``observed'' galaxy catalogs.
We can then apply the full clustering measurement machinery 
(including corrections for varying completeness) to these catalogs
and apply our cosmological inference tools 
to understand the impact of observational systematics on
cosmology from the WFIRST GRS.
As with the weak lensing investigation, we will investigate computational
requirements beyond FY20 and techniques to reduce them. We will also make our
simulations publicly available so that others can develop and
test their own methods, with some of them released in the form of blind
data challenges.

\subsection{Systematics Testing and Mitigation (D8)}
%================================================
%\Auth{Shirley, Olivier}
\label{sec:gal_syst}
\input{subsection_clustering_sys}

%\bi
%\item Describe BOSS current techniques
%\ei
%Similarly to weak lensing, the galaxy clustering measurements are susceptible to
%observational and theoretical systematic effects. SIT will ensure that these    
%systematics in the key clustering measurements,such as the BAO and RSD in the   
%two-point correlation function, are are sub-dominant and don't bias the         
%recovered DE constraints. Below we briefly discuss the major systematic effects 
%anticipated for the BAO and RSD and possible mitigating techniques and          
%robustness tests.                                                               
%                                                                                
%{\it BAO systematics}: BAO measurements are expected to be relatively           
%systematics free. Analytical calculations, verified by direct numerical         
%simulations, have found the nonlinear evolution of the density field alters the 
%BAO scale by less than $0.5\%$ at the present epoch (REF by Nikhil, Martin) ,   
%and even less at the higher redshifts probed by WFIRST. A mis-calibrations in   
%the acoustic scale would affect principally the determination  of the Hubble    
%constant, not the dark energy constraints \citep{2004PhRvD..70j3523E}. Galaxy   
%formation may also result in an additional shift in the BAO scale due to        
%mismatched weighting of high and low density regions. Initial perturbative and  
%numerical work also find these shifts to be small, with the most extreme shifts 
%less than $0.5\%$ (Eisenstein 08, Tojeiro 14, Ross 15). The ``reconstruction''  
%of the density field my reduce these effects below 0.1\% (Eisenstein, Seo,      
%Spergel, Sirko 08, Padmanabhan et al. 12, Vargas-Magana, Ho 14). We will use    
%mock catalogues with known input to check that this is indeed the case for      
%WFIRST samples. We will propagate the BAO measurements all the way through the   
%science analysis pipeline and verify that the resulting DE constraints are      
%unbiased. WFIRST will have multiple galaxy types in the overlapping volume will 
%give us an additional handle on testing the robustness of measurements, since   
%the BAO signature is expected to be the same for all samples.                   
%                                                                                
%{\it RSD systematics}: The major systematic effect for the RSD measurements is  
%the theoretical modeling of various nonlinear effects (nonlinearities in real  
%to redshift space mapping, in growth of structure, and in galaxy biasing). It's 
%also possible that the velocity bias will be significant for WFIRST samples.    
%These effects cumulatively were found to be at $0.5\sigma$ (Samushia et al.     
%2014, Alam, Ho et al. 2015) in BOSS data. Possible observational systematics    
%include the effect of uncertainty in the determination of radial selection      
%function $n(z)$ which will result in apparent reduction of the signal.  Loss of 
%galaxies due to slitless-spectroscopy is also an anisotropic effect and may     
%affect the RSD significantly. SIT will study this issues using high-fidelity    
%simulations with known cosmology. Many of the systematics will be less severe   
%for WFIRST compared to current surveys. For example, the non-linear effects in  
%growth will be small due to high redshift of the sample. The $n(z)$ will        
%similarly be much better determined due to high volume and number density.    
%
%


