%
% ** SECTION 3 **
%

\Oli{In this section, we summarize the deliverables we promissed and
what we actually accomplished}

In \S\S \ref{sec:reqt_philosophy},\ref{sec:wl_gal-clusters},\ref{sec:gc}, we
describe our work plan and explain how we will iteratively flow down science objectives to the
measurements to be conducted, develop observational strategies,
simulate synthetic astronomical `truth' data and the observational
data output (including calibration), develop a methodology for
validating dark energy constraints, and define scientific performance
requirements and a complete plan for the science investigation. 
%Our work plan maps the six SIT tasks into the deliverables below. For each deliverable, we identify in parentheses the required tasks (numbered \textit{T 1-6} as in \S 3.1 of the WFIRST SIT call). We will also associate explicitly the sections of our proposal to the deliverables. 
Our work plan maps the six SIT tasks,  identified in parentheses  (numbered \textit{T 1-6} as in \S 3.1 of the WFIRST SIT call), to the deliverables below. 
%For each deliverable, we identify in parentheses the required tasks. 
We also explicitly reference  the deliverables (D1-12) in the section titles of our proposal. 

%a given deliverable it encompasses.
%  For each
% deliverable, 

%  In
% order to map our work plan into the six SIT tasks and our list of
% deliverables, we explicitly associate the subsequent sections with
% these deliverables. 

\subs{$\bullet$ (D1) Full requirements flow-down} from the high-level science goals of the
HLS galaxy clustering and weak lensing survey to detailed performance
of the telescope, wide field instrument, software, operations, and
data transfer.  We will evaluate the mission design, as prepared for
the Critical Design Review (CDR), against these requirements (\textit{T1, T3, T4}). 

\subs{$\bullet$ (D2) Forecasts of the cosmological performance of the HLS Imaging and
Spectroscopy data sets}, including expected constraints on dark energy,
modified gravity, neutrino masses, and inflation, from analyses that
include the measurement of the location of the Baryon Acoustic
Oscillations (BAO), Redshift-Space Distortions (RSD), galaxy power
spectrum and higher order statistics, cosmic shear, galaxy-galaxy
lensing, and cluster demographics. These forecasts will incorporate realistic assessments of observational
systematics and theoretical modeling systematics, and they will examine the expected constraints from different probes individually,
in concert with each other, and in concert with expected constraints
from the WFIRST supernova program, CMB experiments, and other cosmological
surveys such as DESI, LSST, and Euclid.  
We will use our forecasting tools to investigate trades,
e.g., the impact of survey or instrument design choices (area, depth,
pixel size, spectral resolution, etc.) on cosmological performance. (\textit{T1, T2})

\subs{$\bullet$ (D3) Simulated imaging and spectroscopic data sets} for testing pipeline
performance and evaluating systematic biases --- e.g., from confusion,
noise, and incompleteness in images and spectra, or errors in Point
Spread Function (PSF) determination or shape measurement.
These data sets will be created with varying levels of complexity
in the source catalogs and instrumental effects, to allow isolation
of individual contributions to statistical and systematic uncertainties.
Some of these artificial data sets will be made publicly available,
and some will take the form of data challenges, where the underlying
parameters are initially known only to the creators of the data set,
in the spirit of the Shear Testing Program (STEP) and Gravitational
Lensing Accuracy Test (GREAT) weak lensing data
challenges \cite{Heymans2006, Massey2007, Bridle2010, Kitching2012, Mandelbaum2015}. 
 (\textit{T3, T5})

\subs{$\bullet$ (D4) Proto-type imaging and spectroscopic pipelines}, including weak lensing
shape measurement and galaxy redshift measurement, tested against the
above artificial data sets.  These proto-type pipelines will provide
building blocks for development of full pipelines during the implementation
phase, and they will allow us to sharpen definitions of software
requirements and to identify challenges to and strategies for meeting
these requirements. (\textit{T3, T5})

\subs{$\bullet$ (D5) Calibration strategies} for photometry, shape measurement, spectroscopy,
and redshift completeness.  Evaluation of the expected performance of these
strategies against the science requirements. (\textit{T4})

\subs{$\bullet$ (D6) A strategy for the determination and calibration of photometric redshifts}
using WFIRST data and anticipated external data (e.g., LSST optical
photometry), and defining ground-based data that are needed to
implement this strategy (e.g., spectroscopic training sets, large
redshift surveys for calibration via cross-correlation).
Evaluation of the impact of remaining photometric redshift uncertainties
on statistical and systematic errors in weak lensing and clustering analyses.
Definition of requirements for WFIRST photometric redshifts informed
by this strategy and evaluation. \textit{(T4)}

\subs{$\bullet$ (D7) A detailed operations concept for the HLS Imaging and Spectroscopy 
program,} extending the work presented in SDT13 and SDT15. \textit{(T2, T6)}

\subs{$\bullet$ (D8) Development of methods for modeling and interpreting the cosmological
measurements anticipated from WFIRST}. 
%These methods will require discussing 
Determination of the effects of non-linear gravitational clustering, realistically complex relations between the
galaxy and dark matter distributions, and the influence of the baryon
component on matter clustering. 
%We will also study techniques to
The study of techniques to
remove systematic biases, e.g., by marginalization over nuisance
parameters. 
%Methods investigated will include 
Utilization of cosmic shear,
galaxy-galaxy lensing, cluster mass functions and cluster weak lensing, BAO, RSD, the galaxy
power spectrum, and higher order statistics for galaxy clustering, weak
lensing, and various combinations.
%We will identify 
Identification of areas where
further improvements of theoretical modeling would significantly
enhance the cosmological return from WFIRST. \textit{(T3)}

\subs{$\bullet$ (D9) Simulated light-cone observations} based on cosmological simulations for
guiding this methodology development and testing its performance.
Most of these data sets will be at the level of galaxy redshift and shape
catalogs rather than the pixel-level imaging and spectroscopy simulations
described above.  They will incorporate varying degrees of complexity
regarding galaxy bias, redshift evolution, survey geometry, and
observational systematics such as incompleteness, shape measurement errors,
and photometric redshift biases.  Many of these artificial data sets
will be made publicly available, and some will take the form of data
challenges, where the underlying parameters are initially known only
to the creators of the data set. \textit{(T3, T5)}

\subs{$\bullet$ (D10) 
%A proposed set of pilot surveys 
Pilot survey proposals with associated figures of merits,} to be executed during the first
months of WFIRST operations. These would become part of the final
dark energy data set but also pin down remaining astrophysical or
instrument performance uncertainties at the level needed to optimize 
the HLS. We will develop the figures of merit required to quickly
assess the data-quality and make operational decisions regarding the
cosmological surveys. \textit{(T2, T6)}

\subs{$\bullet$ (D11) A prioritized program of observations from other facilities,}
ground and space-based, needed to calibrate or finalize 
strategy decisions on the WFIRST dark energy program. \textit{(T6)}

\subs{$\bullet$ (D12) Broad engagement with the cosmological community}, through workshops,
talks, publications, and public release of codes and artificial data sets, with the
goals of (a) building awareness of and broad support for the WFIRST
dark energy program and (b) inspiring the community to develop methods
and carry out investigations that will maximize the cosmological
return from WFIRST. \textit{(T6)}

